### 2017-08-09 Paper01_EnthalpyAndCrystallization.tex
Results - annealing xrd - added references to the table, turned off cross refecning

%\documentclass[a4paper,12pt,oneside]{article}%FinalView
\documentclass[draft,a4paper,12pt,oneside]{article}%draftView

\input{settings/preamble.tex}%Inputs Preamble for its .tex
\usepackage[color]{showkeys}%Shows cross ref paths

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c }
		\toprule
		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
		& First Temp & Last Temp & First Temp & Last Temp \\
		\midrule
		Glass 						& 35 & 200 & 35 & 200 \\
		Mg$_{51}$Zn$_{20}$ \cite{Zhang2013, Khan1989} & 170 & 200 & 140 & 200 \\
		Mg 							& 170 & 320 & 140 & 320 \\
		Ca$_{2}$Mg$_{5}$Zn$_{5}$ \cite{Zhang2013, Cao2016} & 200 & 250 & 200 & 250 \\
		MgZn \cite{Khan1989} & 250 & 250 & 250 & 250 \\
		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013} & 290 & 320 & 290 & 320 \\
		\bottomrule
	\end{tabular}
	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
	\label{tab:Crystal_Sequence}
\end{table}

>>>>

\documentclass[a4paper,12pt,oneside]{article}%FinalView
%\documentclass[draft,a4paper,12pt,oneside]{article}%draftView

\input{settings/preamble.tex}%Inputs Preamble for its .tex
%\usepackage[color]{showkeys}%Shows cross ref paths

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c }
		\toprule
		Phase & \multicolumn{2}{c}{Bulk} & \multicolumn{2}{c}{Film}                 \\
		& First Temp & Last Temp & First Temp & Last Temp \\
		\midrule
		Glass 						& 35 & 200 & 35 & 200 \\
		Mg$_{51}$Zn$_{20}$ \cite{Zhang2013, Khan1989} & 170 & 200 & 140 & 200 \\
		Mg 							& 170 & 320 & 140 & 320 \\
		Ca$_{2}$Mg$_{5}$Zn$_{5}$ \cite{Zhang2013, Cao2016} & 200 & 250 & 200 & 250 \\
		MgZn \cite{Khan1989} & 250 & 250 & 250 & 250 \\
		Ca$_{2}$Mg$_{5}$Zn$_{13}$ \cite{Zhang2013, Zhang2012, Zhang2011} & 290 & 320 & 290 & 320 \\
		\bottomrule
	\end{tabular}
	\caption{Temperatures at which each crystallisation phase is first observed and last observed in the annealing \acrshort{xrd} for both the bulk and film. All temperatures are in \degree C.}
	\label{tab:Crystal_Sequence}
\end{table}
